---
title: "connectivity_analysis"
output: html_notebook
author: ruonan jia
time: 6.18.2019
---



---
load packages
```{r}
library(ggplot2)
library(ez)
library(psych)
library(lme4)
```

---
functions
```{r}
data_summary <- function(data, varname, groupnames){
  # Function to calculate the mean and the standard error
  # for each group
  #+++++++++++++++++++++++++
  # data : a data frame
  # varname : the name of a column containing the variable
  #to be summariezed
  # groupnames : vector of column names to be used as
  # grouping variables
  
  require(plyr)
  summary_func <- function(x, col){
    c(mean = mean(x[[col]], na.rm=TRUE),
      sd = sd(x[[col]], na.rm=TRUE)/sqrt(length(x[[col]])))
  }
  data_sum<-ddply(data, groupnames, .fun=summary_func,
                  varname)
  data_sum <- rename(data_sum, c("mean" = varname))
  return(data_sum)
}

```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
