---
title: "connectivity_analysis"
output: html_notebook
author: ruonan jia
time: 6.18.2019
---



---
load packages
```{r}
library(ggplot2)
library(ez)
library(psych)
library(lme4)
```

---
functions
```{r}
data_summary <- function(data, varname, groupnames){
  # Function to calculate the mean and the standard error
  # for each group
  #+++++++++++++++++++++++++
  # data : a data frame
  # varname : the name of a column containing the variable
  #to be summariezed
  # groupnames : vector of column names to be used as
  # grouping variables
  
  require(plyr)
  summary_func <- function(x, col){
    c(mean = mean(x[[col]], na.rm=TRUE),
      sd = sd(x[[col]], na.rm=TRUE)/sqrt(length(x[[col]])))
  }
  data_sum<-ddply(data, groupnames, .fun=summary_func,
                  varname)
  data_sum <- rename(data_sum, c("mean" = varname))
  return(data_sum)
}

```

---
load data
```{r}
behav_path <- "D:/Ruonan/Projects in the lab/VA_RA_PTB/Clinical and behavioral"
image_path <- "D:/Ruonan/Projects in the lab/VA_RA_PTB/Imaging analysis/Imaging_anallysis_082018"
setwd(behav_path)

# load('data_all_noFemale_05122019.rda')
# load('data_all_noPCA_04092019.rda')
load("data_all_noFemale_day1day2_05122019.rda")
# load("data_all_day1day2_04082019.rda")

pcl <- read.csv('pcl.csv',header = TRUE)
demo <- read.csv('ed_income.csv', header = TRUE)
demo$education <- factor(demo$education, order = TRUE, levels = c(1,2,3,4,5,6))
demo$income <- factor(demo$income, order = TRUE, levels = c(1,2,3,4,5,6,7,8,9,10))

setwd(image_path)
conn <- read.csv('connectivity_capsvmPFC_GilaieDotanrPPC.csv', header = TRUE)

```


---
merge data
```{r}
tball_pcl <-  merge(tball, pcl, by = 'id')
tb_all <- merge(tball_pcl, demo, by = 'id')
tb = tb_all[tb_all$isExcluded_imaging==0 & tball$isMale==1,]

conn_tb <- merge(conn, tb, by = 'id')
```

---
plot correlation
```{r}
#x2plot = 'pcl5_total'
x2plot = 'total_pm'
y2plot <- 'conn'

conn_plot <- conn_tb[conn_tb$isDay1 == 1 & conn_tb$isGain == 1 & !conn_tb$group == 'R' & conn_tb$isMal==1 & conn_tb$isExcluded_imaging == 0, ]


ggplot(conn_plot, aes(x=eval(parse(text = x2plot)), y=eval(parse(text = y2plot)))) + 
  geom_point(size=5) +
  geom_smooth(method=lm, se=TRUE, linetype="dashed", color = "black") + 
  scale_x_continuous(breaks = c(0, 20, 40, 60, 80, 100, 120), limits = c(0,120)) +
  #scale_y_continuous(limits = c(-0.6,0.4)) +
  theme_classic() +
  theme(text = element_text(size=20),
        axis.line = element_line(size = 1.5)) +
  xlab(x2plot) + ylab(y2plot)

test <- corr.test(x=conn_plot$total_pm,
          y=conn_plot$conn,
          use = "pairwise",
          method = "spearman",
          adjust = "none",
          alpha=.05
)
test

```


---
plot group difference
```{r}
conn_plot <- data.frame(conn_tb$id, conn_tb$isGain, conn_tb$isExcluded_imaging, conn_tb$isMale, conn_tb$group, conn_tb$conn)

names(conn_plot) <- c('id', 'isGain', 'isExcluded_imaging', 'isMale', 'group', 'conn')

y2plot = "conn"
x2plot = "total_pm"

tb2plot <- data_summary(conn_plot[conn_plot$isGain == 0 & conn_plot$isExcluded_imaging == 0 & conn_plot$isMale == 1 & !conn_plot$group == 'R',],varname= y2plot,groupnames=c("group"))


# group 
ggplot(data=tb2plot,aes(x=group, y=eval(parse(text = y2plot)), fill=group)) + 
  geom_bar(stat="identity", position=position_dodge()) +
  geom_errorbar(aes(ymin=eval(parse(text = y2plot))-sd, ymax=eval(parse(text = y2plot))+sd), width=0.2, position=position_dodge(0.9)) +
  scale_fill_manual(values = c('#228B22', '#FF8C00'), labels = c('Control', 'PTSD')) +
  theme_classic() +
  scale_x_discrete(name = 'Group', limits=c("C", "P"), labels=c("Control","PTSD")) +
  labs(title=paste('SV',y2plot), y = "Connectivity")
```



Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
